% Created 2015-02-08 Sun 22:35
\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\setlength\parindent{0pt}
\usepackage{titling}
\addtolength{\topmargin}{-1.375in}
\addtolength{\textheight}{1.75in}
\addtolength{\oddsidemargin}{-.375in}
\addtolength{\evensidemargin}{-.875in}
\addtolength{\textwidth}{0.75in}
\author{Michael Hunsinger}
\date{\today}
\title{Assignment Two}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.4.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle

\section*{Question One}
\label{sec-1}
\subsection*{Derivation}
\label{sec-1-1}
You will find the derivation tree below for the modified Missionaries and
Cannibals problem, with four membors of each party. A small problem arises
since the boat's capacity is \emph{n - 1}, where \emph{n} is the members of one party,
and both partys have \emph{n} members. \\

Assume the same starting conditions, where \emph{c} is the number of cannibals and
\emph{m} is the number of missionaries on the target side of the river. All
cannibals and missionaries are on the starting side of the river, thus \emph{c =
0} and \emph{m = 0}.

\begin{equation}
\begin{split}
S(c, m) \rightarrow^1 & A(1,1) \\
\rightarrow^2 & p(1,1)A(3,0) \\
\rightarrow^2 & p(1,1)p(3,0)A(2,2) \\
\rightarrow^2 & p(1,1)p(3,0)p(2,2)A(1,3) \\
\rightarrow^2 & p(1,1)p(3,0)p(2,2)p(1,3)A(2,3) \\
\rightarrow^2 & p(1,1)p(3,0)p(2,2)p(1,3)p(2,3)A(3,3) \\
\rightarrow^2 & p(1,1)p(3,0)p(2,2)p(1,3)p(2,3)p(3,3)A(3,4) \\
\rightarrow^2 & p(1,1)p(3,0)p(2,2)p(1,3)p(2,3)p(3,3)p(3,4)A(4,4) \\
\rightarrow^3 & p(1,1)p(3,0)p(2,2)p(1,3)p(2,3)p(3,3)p(3,4)p(4,4) \\
\end{split}
\end{equation}

\subsection*{Grammar}
\label{sec-1-2}
Below is the general controlled grammar for the Missionaries and Cannibals
problem. Most of the changes occur in the functions and predicates.

Let \emph{c} be the number of cannibals and \emph{m} be the number of missionaries on
the target side of the river, and \emph{n} be the number of members in each
party. If we assume the capacity of the boat is also \emph{n}, then much of the
problem stays the same.

\begin{center}
\begin{tabular}{rllll}
L & Q & Kernel & F$_{\text{T}}$ & F$_{\text{F}}$\\
1 & Q$_{\text{1}}$ & S(c,m) $\rightarrow$ A(c + 1, m + 1) & \{2\} & \varnothing\\
2 & Q$_{\text{2}}$ & A(c,m) $\rightarrow$ p(c, m)A(f$_{\text{1}}$(c,m), f$_{\text{2}}$(m)) & \{2\} & \{3\}\\
3 & Q$_{\text{3}}$ & A(c,m) $\rightarrow$ p(c, m) & \varnothing & \varnothing\\
\end{tabular}
\end{center}

\begin{itemize}
\item Predicates
\begin{itemize}
\item \emph{Q$_{\text{1}}$} = true
\item \emph{Q$_{\text{2}}$(c, m)} = true if $(c > 0 \wedge c < n) \vee (m > 0 \wedge m < n)$
\item \emph{Q$_{\text{3}}$(c, m)} = false if $(c = n \wedge m = n) \vee ((c > m) \vee (3 - c) >
       (3 - m))$
\end{itemize}
\item Functions
\begin{itemize}
\item The functions stay the same as well, only replacing \emph{n} where there are /3/s.
\end{itemize}
\end{itemize}

\section*{Question Two}
\label{sec-2}
\subsection*{Grammar}
\label{sec-2-1}
Below is a derivation for the Tower of Hanoi with four pivots and \emph{n} disks.

\begin{center}
\begin{tabular}{rllll}
L & Q & Kernel & F$_{\text{T}}$ & F$_{\text{F}}$\\
1 & Q$_{\text{1}}$ & S(n,x,y,z) $\rightarrow$ A(n,x,y,z) & \{2\} & \varnothing\\
2 & Q$_{\text{2}}$ & A(n,x,y,z) $\rightarrow$ A(f$_{\text{1}}$(n),x,f$_{\text{2}}$(x,y,z),z),$\backslash$\p(n,x,y,z)A(f$_{\text{1}}$(n),f$_{\text{2}}$(x,y,z),y,z) & \{2\} & \{3\}\\
3 & Q$_{\text{3}}$ & A(n,x,y,z) $\rightarrow$ p(n,x,y,z) &  & \\
\end{tabular}
\end{center}

\subsection*{Derivation}
\label{sec-2-2}
% Emacs 24.4.1 (Org mode 8.2.10)
\end{document}
